Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-23 krs-survey.tex
Added reference to Ke Jia project (wrighteagle)

One important exception if the \emph{Negation as failure} inference rule, as
implemented by {\sc Prolog} for instance, that allows for non-monotonicity, but
only \emph{within the closed world assumption}.

\fxfatal{Give here an example of non-monotonic reasoning with Prolog}

@@

\subsubsection{Interaction with other agents}
\label{sect|interactions}

@@

\paragraph{Language integration}

@@

@@

\begin{landscape}
\begin{table}
\begin{center}
\rowcolors{2}{lightgray}{codegray}

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMRKF & & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe/?mid=symbolic_reasoning} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia & & Chen et al. \par (Univ. of Science and Technology of China) & & & & & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

\hline

%\end{tabularx}
\end{tabular}
\end{center}
\caption{List of surveyed systems. Projects are listed by category (\emph{KRS} for systems that are explicit knowledge representation and reasoning modules, \emph{Ubiquitous} for systems where knowledge processing is fully distributed, \emph{Language} for languages used as KRS on robots), then names.}
\label{table|surveyed-systems}
\end{table}
\end{landscape}

@@

@@

\begin{tabular}{cp{4.5cm}ccccccccc}
\toprule
\multicolumn{2}{c}{\bf Category} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Golog} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} \\

@@

\multirow{5}{0.7cm}[-0.2cm]{\turn[1.5cm]{90}{\bf Expressive power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  &  &  & & Horn clauses \\
 & Expressive power & & & & & & & &  \\
 & OWA/CWA & CWA & OWA & & & & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Representation of space & & & & & & & & ++  \\
 & Representation of temporality & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & & & & +  \\
 & Knowledge structure alteration & & ++ & & & & & &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & & & &  \\
 & Presupposition accomodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & & & & + \\
 & Learning & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & & & & & & & ++ & ++ \\
 & Interaction & & +++ (external) & & & & & +++ & \\
 & Instanciation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & + & + \\
 & ...with executive layers & & & & & & & + & ++ \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & & & & \\

>>>>

One important exception is the \emph{negation as failure} inference rule, as
implemented by {\sc Prolog} for instance, that allows for non-monotonicity, but
only \emph{within the closed world assumption}.

\fxfatal{Give here an example of non-monotonic reasoning with Prolog}
\fxwarning{Do we mention here Answer Set Programming?}

@@

@@

@@

\subsubsection{Language Processing}
\label{sect|nlp}

@@

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & {\bf Reasoner} & Main reference \\
\midrule
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & KRS & Mavridis, Roy \par (MIT MediaLab) & & ? & & & \cite{Mavridis2006} \\
OMRKF & KRS & Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe/?mid=symbolic_reasoning} & ? & Horn Clauses & ? & \cite{Suh2007} \\
Ke Jia Project & KRS & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP & ASP & ASP & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

\end{tabular}
\end{center}
\caption{List of surveyed systems. Projects are listed by category (\emph{KRS} for systems that are explicit knowledge representation and reasoning modules, \emph{Ubiquitous} for systems where knowledge processing is fully distributed, \emph{Language} for languages used as KRS on robots), then names.}
\label{table|surveyed-systems}
\end{table}
\end{landscape}

@@

\subsection{Ke Jia Project}
\label{sect|kejia}

The Ke Jia project~\cite{Chen2010} integrates on a mobile platform a knowledge
representation language with natural language processing, task planing and
motion planing.

Knowledge representation relies on \emph{Action Language C}, itself based on
\emph{Answer Set Programming} (ASP)~\cite{Gelfond2008}. These languages, that
are syntactically close to Prolog, are based on \emph{stable models} of logic
programs, and support non-monotonic reasoning. Default and non-monotonic
reasoning has been especially researched within the Ke Jia project for symbolic
task planing~\cite{Ji2011} and underspecified natural language processing.

Amongst other features, the natural language processing capabilities of the
system support acquisition of new logical rules at run-time.

\paragraph{Experiments} The Ke Jia robot has been demonstrated in several tasks
involving human-robot interaction with natural language. These tasks include a
task with multiple \emph{pick \& carry} that are globally optimized, naive
physics reasoning via teached rules or more complex scenarii with the robot
delivering drinks, taking into account changing and mutually exclusive
preferences of users.

@@

\begin{tabular}{cp{4.5cm}ccccccccc}
\toprule
\multicolumn{2}{c}{\bf Category} & {\sc KnowRob} & {ORO} & {\sc PEIS} & {\sc CAST} & {\sc Ke Jia} & {\sc NKRL} & {\sc GSM} & {\sc OMRKF} \\

@@

\multirow{5}{0.7cm}[0.2cm]{\turn[1.5cm]{90}{\bf Expr. power}} & Logical formalism & Prolog & OWL-DL & {\sc CycL} &  & ASP &  & & Horn clauses \\
 & OWA/CWA & CWA & OWA & & & CWA & & & \\
 & Modeling uncertainty & +++ (extension) & & & & & & ++ (stochastic) & + (\emph{candidate} entities) \\
 & Meta-cognition & ++ & ++ & & & & & & \\
\hline
\multirow{6}{0.2cm}{\turn{90}{\bf Model}} & Space Representation & & & & & & & & ++  \\
 & Time representation & & & & & & & + (snapshots) & +  \\
 & Context & & & & & & & & ++  \\
 & Alternative worlds & & +++ & & & & ++ & &  \\
 & Introspection & + (SRDF) & & & & & & &  \\
 & Memory models & & + & & & & & &  \\
\hline
\multirow{10}{0.2cm}{\turn{90}{\bf Reasoning}} & Standard FOL reasoning & +++ & +++ & & & +++ & & & +  \\
 & Knowledge structure alteration & & ++ & & & ++ & & &  \\
 & Lazy evaluation & +++ & & & & & & &  \\
 & Reasoning under uncertainty & ++ (extension) & & & & & + & & \\
 & Non-monotonic reasoning & & & & & +++ & & &  \\
 & Presupposition accomodation & & & & & & & +++ & \\
 & Prediction, projection, diagnosis & & & & & & & & \\
 & Physics-based reasoning & +++ (extension) & & & & & & &  \\
 & Planning & + & +++ (external) & & & ++ & & & + \\
 & Learning & & & & & & & &  \\
\hline
\multirow{3}{0.7cm}{\turn[1cm]{90}{\bf Knw. acq.}} & Acquisition techniques & & & & & & & & \\
 & Grounding & & ++ (external) & & & & & ++ & ++ \\
 & Instanciation & & & & & & & & \\
\hline
\multirow{4}{0.2cm}{\turn{90}{\bf Integ.}} & ...with sensori-motor layers & & & & & & & + & + \\
 & ...with executive layers & & & & & & & + & ++ \\
 & NLP & & +++ (external) & & & +++ & & +++ & \\
 & Monitoring and debugging & & & & & & & & \\
 & Performances & & & & & + & & & \\
